Draft: Learning Laplacian from Binomial Signals

### 2022-03-15 draft.Rmd
Updates to draft.

---
title: 'Draft: Learning Laplacian from Binomial Signals'
author: "Skip Moses"
date: "3/12/2022"
output: html_document
bibliography: ref.bib 
cls: IEEEtran.cls
---

@@

Note that \ref{eq:quadraticform} is minimized when adjacent vertices have identical signal values. This makes \ref{eq:quadraticform} well suited for measuring the smoothness of a signal on a graph. We can cast the problem of learning a graph by the optimization problem found in \cite{kalofolias2016learn}
\begin{equation}
	\label{eq:GLP}
	\begin{aligned}
		\min_L       & \phantom{..} \text{tr}(Y^TLY) + f(L), \\
		\textrm{s.t.}& \quad \text{tr}(L) = N,\\
		& \quad L_{i,j} = L_{j,i} \leq 0, \phantom{..} i \neq j, \\
		& \quad L\cdot \textbf{1} = \textbf{0}
	\end{aligned}
\end{equation}

>>>>

---
title: 'Draft: Learning Laplacian from Binomial Signals'
author: "Skip Moses"
date: "3/12/2022"
output: pdf_document
bibliography: ref.bib 
cls: IEEEtran.cls
---

@@

Note that \ref{eq:quadraticform} is minimized when adjacent vertices have identical signal values. This makes \ref{eq:quadraticform} well suited for measuring the smoothness of a signal on a graph. We can cast the problem of learning a graph by the optimization problem found in @kalofolias2016learn
\begin{equation}
	\label{eq:GLP}
	\begin{aligned}
		\min_L       & \phantom{..} \text{tr}(Y^TLY) + f(L), \\
		\textrm{s.t.}& \quad \text{tr}(L) = N,\\
		& \quad L_{i,j} = L_{j,i} \leq 0, \phantom{..} i \neq j, \\
		& \quad L\cdot \textbf{1} = \textbf{0}
	\end{aligned}
\end{equation}

## Our Model

In order to generalize our model, we will take inspiration from the ideas used to generalize linear regression to logistic regression. Let $p(x = 1)$ be the probability a signal value of $1$ is observed on node $x$. Our model will be of the form 
\begin{align}
\text{logit}(p) = \chi h + p(x = 1) + \epsilon
\end{align}

Where $\chi$ is our matrix of eigenvalues for our graph. Recall, in binomial distribution the expectation is exactly $p(x = 1)$.

## Discussion

Currently, GSP frameworks such as ours have limitations making them only practical in experimental settings. For instance, these frameworks require the input to be the entire graph. This automatically puts a harsh limit on the size of the graphs that can be learned. Another related limitation, is the availability of the algorithms used to learn the laplacian. In @saboksayr2021accelerated the author shows fast proximal-gradient iterations can be applied to the framework given by @kalofolias2016learn converges to a globally optimal solution in $O (1/k)$. A natural next step would be to apply fast proximal-gradient iterations our framework to overcome scalability issues.

## References
<div id="refs"></div>
